### 2011-02-22 trunk/deliverables/D2_2_Ontology/fast_d2_2_3_ontology.tex
final version
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1280 d8b0c59b-6544-0410-94d9-83a5658a058e

All relevant properties of the FAST conceptual model are listed in Tab.~\ref{tab:glossary_of_terms_properties}. Not all properties which will eventually be defined in the formal ontology are listed in the table: in many cases, these concrete properties simply reflect particular instances of generic composition or aggregation relations, which become apparent in the diagrams in Sect.~\ref{ssub:term_relations_within_the_conceptual_model}. Usually, these concrete properties will follow a general naming scheme of \texttt{hasCLASS\_NAME}, e.g., \texttt{hasDefinition} or \texttt{hasPreCondition}.

@@

In FAST, resources (gadgets, screenflows, screens and their components) exist in different stages throughout their lifecycle. Moving top-down from the high-level conceptual description to gadgets in use at runtime, the following differences can be made in terms of the level of instantiation:

>>>>

All relevant properties of the FAST conceptual model are listed in Tab.~\ref{tab:glossary_of_terms_properties}. Not all properties which will eventually be defined in the formal ontology are listed in the table: in many cases, these concrete properties simply reflect particular instances of generic composition or aggregation relations, which become apparent in the diagrams in Sect.~\ref{ssub:term_relations_within_the_conceptual_model}. Usually, these concrete properties will follow a general naming scheme of \texttt{hasCLASS\_NAME}, e.g., \texttt{hasPreCondition}.

@@

In FAST, all different kinds of entities (gadgets, screenflows, screens and their components) exist in different stages throughout their lifecycle. Moving top-down from the high-level conceptual description to gadgets in use at runtime, the following differences can be made in terms of the level of instantiation:
